Supplementary Materials

### 2019-10-25 sup_mat/sup_mat.Rmd
Made some edits to figure
Fixed Legend label
Changed SHVS to SHLS to be consistent with the paper

plt_acs_logrt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice),
         sdev = sd(RT),
         mean_rt = mean(RT)) %>%
  filter(RT > mean_rt - 3*sdev,
         RT < mean_rt + 3*sdev,
         RT > 300) %>%  
  ggplot(aes(RT,
             colour = Optimal_Choice,
             fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(legend.position = "bottom",
        strip.text.x = element_blank()) + 
  scale_colour_ptol() + 
  scale_fill_ptol() + 
  facet_wrap(~Optimal_Choice)
plt_acs_logrt$labels$x <- "Response Time (msecs)"

@@

## Accuracy 
The results of these experiments show there is no meaningful correlation with how accurate participants were in the ACS and SHVS tasks. Even when breaking the data from the SVHS task into the 3 different trial types, there were still no meaningful correlations.

@@

# average accuracy for each task
acc_ACS <- dat_ACS %>% 
  group_by(SubNo) %>% 
  summarise(Accuracy = mean(Acc)) %>% 
  ungroup() %>% 
  mutate(Task = "ACS",
         participant = SubNo) %>% 
  select(-SubNo)
acc_LS <- ls_acc_RT %>% 
  group_by(observer, targSide) %>% 
  summarise(Accuracy = mean(accuracy)) %>% 
  ungroup() %>% 
  mutate(Task = paste("SHVS_", targSide, sep = ""),
         participant = observer) %>% 
  select(-observer, -targSide)

# plot accuracy across tasks 
dat_all <- rbind(acc_ACS, acc_LS) %>% 
  spread(key = Task,
         value = Accuracy) %>% 
  gather(SHVS_absent:SHVS_hard,
         key = "s_type", 
         value = "acc")
plt_task <- dat_all %>% 
  ggplot(aes(ACS, acc, colour = s_type)) + 
  geom_point() + 
  facet_wrap(~s_type)
# plt_task

>>>>

plt_acs_logrt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice),
         sdev = sd(RT),
         mean_rt = mean(RT)) %>%
  filter(RT > mean_rt - 3*sdev,
         RT < mean_rt + 3*sdev,
         RT > 300) %>%  
  ggplot(aes(RT,
             colour = Optimal_Choice,
             fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(legend.position = "bottom",
        strip.text.x = element_blank()) + 
  scale_colour_ptol(name = "Optimal Choice") + 
  scale_fill_ptol(name = "Optimal Choice") + 
  facet_wrap(~Optimal_Choice)
plt_acs_logrt$labels$x <- "Response Time (msecs)"

@@

## Accuracy 
The results of these experiments show there is no meaningful correlation with how accurate participants were in the ACS and SHLS tasks. Even when breaking the data from the SHLS task into the 3 different trial types, there were still no meaningful correlations.

@@

# average accuracy for each task
acc_ACS <- dat_ACS %>% 
  group_by(SubNo) %>% 
  summarise(Accuracy = mean(Acc)) %>% 
  ungroup() %>% 
  mutate(Task = "ACS",
         participant = SubNo) %>% 
  select(-SubNo)
acc_LS <- ls_acc_RT %>% 
  group_by(observer, targSide) %>% 
  summarise(Accuracy = mean(accuracy)) %>% 
  ungroup() %>% 
  mutate(Task = paste("SHLS_", targSide, sep = ""),
         participant = observer) %>% 
  select(-observer, -targSide)

# plot accuracy across tasks 
dat_all <- rbind(acc_ACS, acc_LS) %>% 
  spread(key = Task,
         value = Accuracy) %>% 
  gather(SHLS_absent:SHLS_hard,
         key = "s_type", 
         value = "acc")
plt_task <- dat_all %>% 
  ggplot(aes(ACS, acc, colour = s_type)) + 
  geom_point() + 
  facet_wrap(~s_type)
# plt_task
